---
title: "Leaflet project"
author: "Xue Zhang"
date: "2019/7/17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Requirements

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## project
The population density of 155 cities in Maryland of the U.S. was shown below. We get the data from https://simplemaps.com/data/us-cities

## reading and cleaning the data
```{r}
data <- read.csv("E:/r/9.Developing Data Products/project1/uscitiesv1.5.csv")
mddata <- data[which(data$state_id=="MD"),c(1,7,8,10,11)]
#mddata <- mddata[complete.cases(mddata),]

```


```{r, echo=TRUE, message=FALSE}
library(leaflet)
md_cities <- data.frame(name = mddata$city,
                        pop = mddata$population_proper,
                        lat = mddata$lat,
                        lng = mddata$lng)
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 2, radius = sqrt(mddata$density) * 30)
```